

#require(superheat)
#require(rword2vec) #and others


###### Purpose

We want to test Google's famous `word2vec` result $\mathrm{king} - \mathrm{man} + \mathrm{woman} = \mathrm{queen}$. This particular result fits our semantic intuition, but how many other equations come as close?



###### Tolerance

Chris wants to make

```{r}
close <- .1
message(close, "should be as close as king - man + woman.")
close -> good.enough

close.but.not.close.enough <- .5
messages("how to index ", close.but.not.close.enough, "? maybe a slider in a sh.")


too.far <- 5
message(too.far, " should be so far out that ridiculous non-results would be inclued if you (fairly) included the spheres of distance ", too.far)
```


## Data sources

- subtitle files
- examples others provide
- Rob: **SAT analogy books!**
- Chris: any equations with more subtraction terms?
- Chris: bring a dictionary



## tests

- Brian: `king - dress + ___ = queen`
- Brian: `king + free movement + ace|killer - monarch = queen`
- `sun - light + dark = moon`
- `sun - day + night = moon`
- `pauper + money = person`
- `rich - wealth = poor`, `rich - money = poor`
- `lemon - yellow + green = lime`
- `seeds + soil + sun = garden` (or `plants`)
- `marker - ___ + wax = crayon` (ink? dye?)
- `Halloween - October + December = Saturnalia`  (←we should be putting in some guesstimate of how valid we think our own tests are. ―Chris)
- 



#### synonymy

- `ink ≈ dye`
- 

grab a (paper) thesaurus and use this to argue about the shades of meaning among synonyms



## graphs
```{r plots}
install.packages('tsne',ask=F,dep=T)
require(tsne)
```


##### desiderata

try to test "shades" of meaning. Rob's example: «it’s pouring» versus «it’s raining» --- pouring is indeed more idiomatic and familiar (Rob’s example: tell someone you’ll be late for a business meeting because it’s pouring? no..)





# Analogies

Rob pointed out that analogies like `calf : cow :: piglet : pig`, etc. But what is really the structure of some of these?

Take `tree : forest :: tire : car`. This analogy might not be accepted as clearly right. Trees are part of a forest—as tires are part of a car. But tires are seen to be a heterogeneous part of a car, whereas a big enough collection of trees is seen to equal a forest. Then again --- trees _are_ a heterogeneous part of a forest, as forests have a canopy — underbrush — frogs — berries — dead pine needles — moss — and so on.








## Ben Schmidt’s google news vectors

Ben Schmidt posted a nice [`word2vec` walkthrough](https://rstudio-pubs-static.s3.amazonaws.com/225114_28f6a67eebce4641901e57201006964c.html).


```{r ben.schmidt}
install.packages('devtools', ask=F, dep=T)
devtools::install_github('someone/wordVectors')
message("get Ben’s weightings")
require(curl)
ben.schmidts.vectors.weighted.from.google.news <- 'http://benschmidt.org/word2vec_workshop/short_google_news.bin'
curl_fetch_disk(ben.schmidts.vectors.weighted.from.google.news, 'ben.schmidts.vectors.short.google.news.bin')
require(wordVectors)
ben.schmidts.vectors.short.google.news.bin
ben.schmidts.short.google.news.model <- read.vectors('ben.schmidts.vectors.short.google.news.bin')
```

## calibration

```{r calibration}

```







#### more corpora

```{r train.weights.more.corpora}
install.packages('janeaustenr',ask=F,dep=T)
```
